PK object batch mode trial

### 2023-06-28 data-raw/batchMode_trial_gpm.Rmd
Added new plot parameters and substituted in`reframe` for the `summarize` call in do_data_info()

my_predata <- subset(cvt,
                     chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                                   "DTXSID2021731"))
```

@@

```{r remaining_methods}
# plot()
# coef_sd
# logLik.pk
# get_tkstats()

>>>>

my_predata <- subset(cvt,
                     chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                                   "DTXSID2021731",
                                                                   "DTXSID5034773",
                                                                   "DTXSID5032600",
                                                                   "DTXSID7022253"))
```

@@

```{r remaining_methods}
# coef_sd
# logLik.pk
# get_tkstats()
